\documentclass{article}
\usepackage{fixltx2e}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width 0.7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[4]{{ \textbf{#1} -- #2 (#3)\\ \underline{\textbf{\emph{#4}}}\\  }}
\newcommand{\contact}[3]{
  \vspace*{-24pt}
\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder 
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 $\bullet$  Selected Coursework:\\
\vspace*{5pt}
}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 \\
}
\newcommand{\reference}[4]{
 \textbf{#1}  #2\\
 \hspace{20pt}  #3\\ 
 \hspace{20pt} #4\newline
}
% END RESUME DEFINITIONS
\usepackage[pdftex]{hyperref}
\hypersetup{colorlinks,%
            citecolor=black,%
            filecolor=black,%
            linkcolor=black,%
            urlcolor=black,%
            pdftex}
\begin{document}

\small
\smallskip
\vspace*{-22pt}

\contact{Keith P. Wyss}
{1278 W 9th Street, Apt 803, Cleveland, OH 44113}
{(412) 760-4997 $\bullet$ WyssMan@gmail.com }

\header{Education}
 \textbf{The University of Pittsburgh} Pittsburgh, PA, U.S.A. \newline%
 $\bullet$ Bachelor of Engineering: Computer Engineering, 2012\\ 
 \hspace{15pt}-- Honors: Summa Cum Laude \newline%
 $\bullet$ Bachelor of Science: Mathematics, 2012\\ 
 \hspace{15pt}-- Honors: Summa Cum Laude \newline%
 \vspace{7pt}
 $\bullet$  Selected Coursework:
\vspace{2pt}
\area{Computer Science}{$\cdot$ Databases $\cdot$ Data Structures %
$\cdot$ Algorithms $\cdot$ Networking $\cdot$ Operating Systems %
 $\cdot$ Artificial Intelligence $\cdot$ Systems Programming %
$\cdot$ Theory of Computation %
$\cdot$ Software Engineering $\cdot$}
\area{Mathematics}{$\cdot$ Calculus $\cdot$ Linear Algebra %
$\cdot$ Discrete Math $\cdot$ Probability and Statistics $\cdot$ Differential Equations %
$\cdot$ Numerical Methods $\cdot$ }
\area{Computer Engineering}{%
$\cdot$ Computer Architecture %
$\cdot$ Advanced Digital Design %
$\cdot$ Linear Circuits %
$\cdot$ Signals and Systems %
$\cdot$ Microelectronics %
}

\header{Employment Experience}
\employer{Explorys Medical}{High Performance Indexing Team} {2012 -- Present} %
{Hadoop Software Engineer}
\begin{achievements}
  \item Worked on the indexing layer of the Explorys codebase, mapping disparate hospital datasets to a unified medical ontology that was published to the applications higher on the stack.
  \item Delivered batch jobs to periodically generate and load store files for a random access health system engine powered by Apache HBase.
  \item Developed and maintained a web service that computed and served the results of set intersection over a large population indexed by feature similarity. 
      \item Wrote a custom MapReduce connector for Apache HBase that outperformed the typical TableInputFormat in some circumstances by a factor of three.
        \item Worked on a trending API to collect production statistics about data completeness and resource consumption and prepare them for graphical consumption.
          \item Participated in a team that designed a new architecture for the Explorys backend, starting with data ingestion and moving through until a published view.
            \item Built operational infrastructure within a unix environment for batch scheduling, event email alerts, and data aggregation.
            \end{achievements}

\employer{Pittsburgh Art House}{Website Creation}{Summer 2011}{Webmaster}
   \begin{achievements}
     \item Designed, programmed, and deployed website for non-profit organization the Pittsburgh Art House. \emph{\href{http://pgharthouse.heroku.com}{Hosted on heroku.}}
       \item Constructed SQL model to serve pictures to the website for Artist profiles and Gallery.
         \item Created the frontend code for the routing and the presentation of the site.
           \item Implemented system of roles emulating unix permissions overtop the routing layer to allow administration of the website without coding knowledge.
             \end{achievements}

\employer{Brackenridge Fellowship}{Fluid Dynamics}{Summer 2010}{Researcher}
\begin{achievements}
  \item Investigated a relationship between time energy dissipation and a simplified ``Pao'' model of fluid turbulence.
    \item Constructed models that used adaptive Runge-Kutta 4/5 and other techniques of Numerical Analysis to solve the equations that arose from a Fourier series representation of the Navier Stokes equations under our initial conditions.
      \item Proved the stability of the models in question, performed complexity analysis of the algorithm, and co-authored the paper listed below.
        \item Performed analysis of the equations, searching for a coupling that could introduce intermittency into the energy flow, while preserving the time averaged logarithmic slope.
\end{achievements}%
\newpage
\header{Refereed Publications}
\begin{achievements}
\item \emph{\textbf{\href{http://www.math.ualberta.ca/ijnamb/Volume-2-2011/No-1-11/2011-01-04.pdf}{A Transfer Theory Analysis of Approximate Deconvolution Models of Turbulence}
}}\\
  co-authored with Dr. W. Layton (PITT) and Dr. M Neda (UNLV)\\
  \footnotesize{International Journal of Numerical Analysis and Modeling, Series B}\\
  \footnotesize{Volume 2, Number 1, Pages 57-72}
\end{achievements}
\header{Technical Certifications}
\begin{achievements}
\item \textbf{Cloudera Certified Developer for Apache Hadoop} \\
\item \textbf{Cloudera Certified Specialist in Apache HBase} \\
\end{achievements}
\header{Skills}
\begin{achievements}
\item Proficient at software development in Java, C, Ruby, Clojure, Matlab, MIPS Assembly.
\item Competence with Hadoop, HBase, Zookeeper, Vertica, SQL, VHDL, HTML/CSS, \LaTeX
\item Experience within a Unix environment, possesses strong shell scripting skills and a familiarily with system monitoring tools.
\end{achievements}
\end{document}

